### 2018-01-18 Physics Notes/AS Level/All/All.tex
Notes update

>>>>

\section{On the move}
\subsection{Speed and velocity}
\subsubsection{Speed}
\textbf{Displacement} - Distance in a given direction\\
\textbf{Speed} - Change of distance per unit time\\
\textbf{Velocity}- Change of displacement per unit time\\
\section{Motion and force}
\subsection{Newton's laws of motion}
\textbf{First law} - Objects either stay at rest or remain in uniform motion unless acted on by a force.\\
\textbf{Second law} - F=ma\\
\textbf{Third law} - Every action has an equal and opposite reaction\\
\textbf{Inertia} - The resistance of an object to change its motion.
\subsubsection{Terminal speed}
The \textbf{drag force} depends on:Inertia
\item The shape of the object
\item Its speed
\item The viscosity of the fluid the object is travelling through
\section{Waves}
\subsection{Waves and vibrations}
\subsubsection{Definitions}
\textbf{Displacement} - The distance and direction of a particle from its equilibrium position\\
\textbf{Amplitude} - The maximum displacement of a particle\\
\textbf{Wavelength} - The least distance between two adjacent vibrating particles with the same displacement and velocity at the same time\\
\textbf{One complete cycle} - From maximum displacement to the next maximum displacement\\
\textbf{Period} - The time for one complete wave to pass a fixed point\\
\textbf{Frequency} - The number of cycles of vibration of a particle per second.
\section{Optics}
\subsection{The diffraction grating}
\subsubsection{Types of spectra}
\paragraph{Continuous spectra}
The spectrum of light from a filament lamp is continuous. The hotter the light source, the shorter the wavelength of the brightest part of the spectrum.
\paragraph{Line emission spectra}
The light from a discharge tube emits light at specific wavelengths, meaning the spectra is of discrete lines. The wavelengths of the light are characteristic of the element that produces the light.
\paragraph{Line absorption spectra}
This is a continuous spectrum with narrow dark lines at certain wavelengths. This could be produced from the light from a filament lamp passing through a glowing gas. The elements in the gas absorb some of the photons, those that have exactly the correct energy to excite an electron.
